---
title: "salvo"
author: "Charles Gallagher"
date: "8/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### First set up our DOE. I did this by editing the txt file parameters.txt directly. Note the model will not run if there are value of zero.

```{r}
para <- names(read.csv("data_inputs.csv"))
parameters <-read.table("parameters.txt")
rownames(parameters)<- para
colnames(parameters)<- c("low", "high", "decimal")
parameters

```

### Once you're cool with that then create a stacked NOLH. 

```{bash engine.opts='-l', echo = F, warning =F, message = F}
stack_nolhs.rb -s 100 -l 512 parameters.txt  > salvo_NOLH.csv
```

### Next due some datacleaning before putting it into our salvo model. We need col names and make the first salvo be us or china. Then we need to write the file to a csv

```{r message=FALSE}
library(tidyverse)
library(gridExtra)
library(grid)

nolh <- read_table2("salvo_NOLH.csv", 
    col_names = FALSE)
dim(nolh)
names(nolh)<- para
nolh<-nolh %>% 
  mutate(first_salvo = ifelse(first_salvo==0, "china","us"))
head(nolh)

write.csv(nolh, "salvo_NOLH.csv")
```

### Ok now run the simulation. This took about 2 mins on my computer at the end it creates csv. Do anaylsis in R or JMP> 

```{r}
in_data<-read_csv("salvo_NOLH.csv") %>% 
  select(-X1)
head(in_data)

in_data$outcome_china<-rep("NA",nrow(in_data))
in_data$outcome_us<-rep("NA",nrow(in_data))
in_data$iter <- rep("NA",nrow(in_data))



for(i in 1:nrow(in_data)){
# Number of Ships, Weapons Systems
china_platform <- in_data$china_platform[i]
us_platform <- in_data$us_offense[i]

# Staying number of hits it can take from enemy
china_staying<- in_data$china_staying_power[i]
us_staying<-in_data$us_staying_power[i]

# Defense strength in num missiles/platform that it can shoot down
china_defense <- in_data$china_defense[i]
us_defense <-in_data$us_defense[i]

# offense strength in num missiles/platform it can fire at enemey
china_offense <- in_data$china_offense[i]
us_offense <-in_data$us_offense[i]

#who fires first 
first_salvo <- in_data$first_salvo[i]

# Scouting ability /targeting effectiveness sigma
china_scouting<-in_data$china_scouting[i]
us_scouting <-in_data$us_scouting[i]


# readiness ability defense ability how prepared are they react 
china_ready<-in_data$china_ready[i]
us_ready <-in_data$us_ready[i]



iter = 0
while(us_platform > 0 && china_platform > 0 ){
iter = iter +1  
if(first_salvo=="china"){
#delta us
delta_us <-((china_scouting * china_offense*china_platform)-(us_ready * us_defense*us_platform))/us_staying
#update platform count
us_platform <- us_platform- delta_us


## Delta China 
delta_china<- ((us_scouting * us_offense*us_platform)-(china_ready * china_defense*china_platform))/china_staying
# update platform number 
china_platform <- china_platform-delta_china

} # end for if us salvo first

if(first_salvo=="us"){
  ## Delta China 
  delta_china<- ((us_scouting*us_offense*us_platform)-(china_ready * china_defense*china_platform))/china_staying
  # update platform number 
  china_platform <- china_platform-delta_china
  
  #delta us
  delta_us <-((china_scouting *china_offense*china_platform)-(us_ready * us_defense*us_platform))/us_staying
  #update platform count
  us_platform <- us_platform- delta_us
  
} #end if for china salvo first

if(first_salvo=="tie"){
  print("I don't know")
}# end tie salvo 
} # end while loop   

### Outfile 
in_data$outcome_china[i]<-china_platform  # the number of ships that c
in_data$outcome_us[i]<-us_platform
in_data$iter[i] <- iter

} # end for loop 

in_data

write.csv(in_data,"salvo_output.csv")
```

```{r}
in_data <- in_data %>% 
  mutate(us_wins = outcome_us > 0)
ggplot(in_data,aes(x=us_wins))+
  geom_bar()
```

```{r}
names(model_data)
```


```{r}

model_data <-in_data %>% select(us_wins, 1:13)
Logit <- glm(formula = us_wins ~ .,
               family  = binomial(link = "logit"),
               data    = model_data)
summary(Logit)




```

```{r}
library(tidymodels)
library(kableExtra)
model_data <- model_data %>% mutate(us_wins =factor(us_wins))

d<-initial_split(model_data,prop = .99)
t<- training(d)


CART_recipe <-
  recipe(us_wins ~., data = model_data) %>%
 # step_normalize(all_numeric()) %>% 
  themis::step_downsample(us_wins ) %>% 
  prep()


############################ fit Models     #########################
CART_spec <- decision_tree() %>% 
  set_engine("rpart") %>% 
  set_mode("classification") %>% 
  translate()

CART_work_flow <- workflow() %>% 
  add_recipe(CART_recipe) %>% 
  add_model(CART_spec)

fit_CART <-fit(CART_work_flow ,model_data)
fit_CART

 finial_test_fit_CART <-CART_work_flow%>%
   last_fit(d) 


metric_CART<-finial_test_fit_CART%>%
   collect_metrics() 
 metric_CART %>% kable()
library(rpart.plot)
fan_tree <-rpart.plot(fit_CART$fit$fit$fit,main = "Decision Tree Predicting USMC Victory",caption = "AUC: .85")



```






```{r}
ggplot(data=in_data, aes(x=us_platform,y=china_platform, fill=us_wins, color= china_scouting))+
  geom_jitter()

ggplot(data= in_data, aes(x=china_scouting, y= china_platform, color = us_wins ))+
  geom_jitter()+
  labs(title = "How the USMC ASM Battalion is Defeated ")+
       xlab("Chinese Scouting Capablity")+
       ylab("Number of Chinese DDGs" )+
       guides(color=guide_legend(title="USMC Victory"))#chineese fdsafd s

ggplot(data= in_data, aes(x=china_scouting, y=outcome_us, color = us_wins ))+
  geom_jitter()

a<-in_data %>% 
  filter(first_salvo =='us') %>% 
ggplot(aes(x=china_scouting, y= us_staying, color = us_wins ))+
  geom_jitter()+
  labs(title ="First Salvo US")

b<-in_data %>% 
  filter(first_salvo =='china') %>% 
ggplot(aes(x=china_scouting, y= china_platform, color = us_wins ))+
  geom_jitter()+
  labs(title = "First Salvo China")

grid.arrange(a,b)

in_data %>% 
  #filter(first_salvo =='china') %>% 
  filter(us_wins == "TRUE") %>% 
ggplot(aes(x=china_scouting))+
  geom_histogram(color="black")+
  labs(title = "Cases When United States Wins with China Scouting")

library(GGally)

ggpairs(in_data %>% select(1:6, us_wins),
        mapping = ggplot2::aes(color = us_wins))

```
```{r}
ggpl
```

